\begin{thebibliography}{9}
\bibitem{cortial}
Cortial, Y., Peytavie, A., Galin, E. and Guérin, E. (2019), Procedural Tectonic Planets. \textit{Computer Graphics Forum}, 38: 1-11. https://doi.org/10.1111/cgf.13614
\bibitem{meister}
D. Meister and J. Bittner, "Parallel Locally-Ordered Clustering for Bounding Volume Hierarchy Construction," in \textit{IEEE Transactions on Visualization and Computer Graphics}, vol. 24, no. 3, pp. 1345-1353, 1 March 2018, doi: 10.1109/TVCG.2017.2669983.
\bibitem{generatedgames}
Wikipedia contributors. (2022, March 20). List of games using procedural generation. In \textit{Wikipedia, The Free Encyclopedia}. Retrieved 06:20, May 19, 2022, from \url{https://en.wikipedia.org/w/index.php?title=List\_of\_games\_using\_procedural\_generation\&oldid=1078237416}
\bibitem{daggerfall}
Brogan, J. (2016, October 5). \textit{The Daggerfall Paradox}. SLATE. Retrieved May 19, 2022, from\\ \url{https://slate.com/technology/2016/10/the-paradox-of-procedurally-generated-video-games.html}
\bibitem{augustus}
Keriew, \textit{Augustus}, (2021), GitHub repository, \url{https://github.com/Keriew/augustus}
\bibitem{rimworld}
Game Developer Conference [GDC]. (2019). \textit{RimWorld: Contrarian, Ridiculous, and Impossible Game Design Methods} [Video]. YouTube. https://www.youtube.com/watch?v=VdqhHKjepiE
\bibitem{palmer}
Palmer, C. I., \& Leigh, C. W. (1934). \textit{Plane and spherical trigonometry}. New York: McGraw-Hill Book Company, Inc. 
\bibitem{keinert}
Keinert, Benjamin  \& Innmann, Matthias \& Sänger, Michael \& Stamminger, Marc. (2015). Spherical Fibonacci Mapping. \textit{ACM Transactions on Graphics}. 34. 1-7. 10.1145/2816795.2818131. 
\bibitem{todhunter}
Todhunter, Isaac. (1886). \textit{Spherical Trigonometry: For the Use of Colleges and Schools} (5th ed.). London: Macmillan and Co.
\bibitem{scratchapixel}
\textit{Ray Tracing: Rendering a triangle}. Scratchapixel 2.0. Retrieved June 6, 2022, from \url{https://www.scratchapixel.com/lessons/3d-basic-rendering/ray-tracing-rendering-a-triangle/barycentric-coordinates }
\bibitem{voronoi}
Pokojski, Wojciech \& Pokojska, Paulina. (2018). Voronoi diagrams – inventor, method, applications. \textit{Polish Cartographical Review}. 50. 141-150. 10.2478/pcr-2018-0009. 
\bibitem{delaunay}
 Delaunay, Boris. (1934). Sur la sphere vide. A la memoire de Georges Voronoi. \textit{Bulletin de l’Academie des Sciences de l’URSS. Classe des sciences mathematiques et naturelles}, Issue 6, pp. 793–800.
 \bibitem{knuth}
 Guibas, L. J., Knuth, D. E., \& Sharir, M. (1992). Randomized incremental construction of Delaunay and Voronoi diagrams. \textit{Algorithmica}, 7(1-6), 381–413. doi:10.1007/bf01758770 
 \bibitem{ma}
Ma,  Yingdong \& Chen, Qian. (2010). Fast Delaunay Triangulation and Voronoi Diagram Generation on the Sphere. \textit{2010 Second World Congress on Software Engineering},  pp. 187-190, doi: 10.1109/WCSE.2010.136
\end{thebibliography}